Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2015-09-13 3dpas_intro.tex
further refinement in the introduction.

\item This {\it survey} is not meant to be complete, either in scope of domains
  covered or types of infrastructure and application surveyed.  They by
  definition represent the interests and experience of the authors.
  \katznote{need to add a note about the dates in which application data was collected?  I'm not sure the numbers are correct today, for example, from ATLAS}

>>>>

\item This {\it survey} is not meant to be complete, either in scope of domains
  covered or types of infrastructure and application surveyed.  They by
  definition represent the interests and experience of the authors. The
  requirements and barriers of applications cited in this paper specific are
  mostly representative of the time their representatives were surveyed
  (2012-2013); this is also true of the quantitative analysis of applications.

  \katznote{need to add a note about the dates in which application data was
    collected?  I'm not sure the numbers are correct today, for example, from
    ATLAS}\jhanote{Fixed. CF ATLAS: I'll ask Kaushik/ATLAS to check}
